Marlowe: financial contracts on blockchain\thanks{This work is part of the Cardano project and is supported by IOHK,~\url{https://iohk.io}}

### 2018-07-26 tex/paper.tex
Update semantics in paper

\begin{haskellcode}
step inp st c@(Pay idpay from to val expi con) os
  | expired (blockNumber os) expi = (st, con, [ExpiredPay idpay from to cval])
  | right_claim =
    if committed st from bn >= cval
      then (newstate, con, [SuccessfulPay idpay from to cval])
      else (st, con, [FailedPay idpay from to cval])
  | otherwise = (st, c, [])
  where
    cval = evalMoney st val
    newstate = stateUpdate st from to bn cval
    bn = blockNumber os
    right_claim =
      case Map.lookup (idpay, to) (rp inp) of
        Just claimed_val -> claimed_val == cval
        Nothing -> False
\end{haskellcode}
By `available' we mean that sufficient commitments have been made and not yet expired to cover the payment; in this 
case, the payment uses the currency allocated by the cash commitments made by \haskellinline{from} that expire the 
earliest.

>>>>

\begin{haskellcode}
step inp st c@(Pay idpay from to val expi con) os
  | expired (blockNumber os) expi = (st, con, [ExpiredPay idpay from to cval])
  | right_claim =
    if ((committed st from bn >= cval) && (cval >= 0))
      then (newstate, con, [SuccessfulPay idpay from to cval])
      else (st, con, [FailedPay idpay from to cval])
  | otherwise = (st, c, [])
  where
    cval = evalMoney st val
    newstate = stateUpdate st from to bn cval
    bn = blockNumber os
    right_claim =
      case Map.lookup (idpay, to) (rp inp) of
        Just claimed_val -> claimed_val == cval
        Nothing -> False
\end{haskellcode}
By `available' we mean that sufficient commitments have been made and not yet expired to cover the payment; in this 
case, the payment uses the currency allocated by the cash commitments made by \haskellinline{from} that expire the 
earliest.
